Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-08-06 paper.tex

\subsection{Varying the number of factors}
Figure~\ref{fig:factors} shows the effect of the number of factors used 
in the ALS optimization for the RFNU method and the synthetic dataset. We do not find a 
clear effect of the number of factors on the accuracy. \todo{Soudabeh, add results for 50 and 800 factors}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
\caption{Effect of the number of factors used in ALS, RFNU method, synthetic dataset.}
\label{fig:factors}
\end{figure}

>>>>

\subsection{Varying the number of factors}
Figure~\ref{fig:factors} shows the effect of the number of factors used 
in the ALS optimization for the RFNU method and the synthetic dataset. We do not find a 
clear effect of the number of factors on the accuracy.
As it shown, number of factors does not have effect on accuracy specially for the training ratios less than 50\% .However, for the training ratios  over than that having less than 3 factors can dramatically effect the accuracy. Notably at training ratio of 90\% the major accuracy gap is observed between the compute accuracy with 2 factors and the 3 factors; 2 factors accuracy is about 40\% lower than 3 factors accuracy.

\begin{figure}[h]
\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
\caption{Effect of the number of factors used in ALS, RFNU method, synthetic dataset.}
\label{fig:factors}
\end{figure}
